Immigration and Onshoring of High-Impact R&D

### 2020-11-12 Presentations/paper_outline.Rmd

---
title: "Immigration and Onshoring of High-Impact R&D"
subtitle: "Research Outline"
author: "Matthias Niggli"
date: "`r Sys.Date()`"
# bibliography: bibliography.bib # throws an error with this markdown version because of the .bib file.
output: html_document
---

>>>>

---
title: "Immigration and Onshoring of High-Impact R&D"
subtitle: "Research Outline"
author: "Matthias Niggli"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
output: html_document
---
